Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-24 Background/lang_aff.tex
finally at 13 pages

\begin{sloppypar}
\noindent{\textbf{Ruby}}
From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability. This is not documented on the library's homepage.
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
\end{sloppypar}
%\input{Background/ruby.tex}

>>>>

\begin{sloppypar}
\noindent{\textbf{Ruby}}
From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
\end{sloppypar}
%\input{Background/ruby.tex}

### 2016-10-24 Background/php.tex
finally at 13 pages

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@xyz.edu';

// example attack string to be 
// injected as the value for
// $_REQUEST['email'] => 
// 's@s.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@xyz.edu AND spc@spc.com
\end{lstlisting}

>>>>

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@example.com';
// example attack string injected as for
// $_REQUEST['email'] => 
// 'abc@example.com\nCC:spc@example.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@example.com AND spc@example.com
\end{lstlisting}

### 2016-10-24 Background/py.tex
finally at 13 pages

f = FeedParser() # Parser.parsestr() 
# also contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)

# attack string => 
# 's@s.com\nBCC:spc@spc.com'
# for form["email"]

# to:s@s.com AND bcc:spc@spc.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

>>>>

f = FeedParser() # Parser.parsestr() 
# also contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)
# attack string => 
# 'abc@example.com\nBCC:spc@example.com'
# bcc:spc@example.com is added to headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

### 2016-10-24 Results/analysis.tex
finally at 13 pages

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

>>>>

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

### 2016-10-24 System/components.tex
finally at 13 pages

\subsubsection{Form Parser}
\label{Comp:FP}
The actual analysis pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the HTML forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as \texttt{method} and \texttt{action}. These dictate the resulting URL for the HTTP request and the method of the HTTP request.
	\item Data about the form input fields, such as their attributes, names, and default values. The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow the system to reconstruct all data necessary for fuzzing the web application.

@@

The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}). This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.

@@

	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

@@

	Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.

@@

\begin{table}[tbp]
	\centering
	\normalsize
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular e-mail}
\sloppy
`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

>>>>

\subsubsection{Form Parser}
\label{Comp:FP}
The actual analysis pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the HTML forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as \texttt{method} and \texttt{action} (URL) for the HTTP request.
	\item Data about the form input fields, such as their attributes, names, and default values. The default values are essential for fields like {\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow the system to reconstruct all data necessary for fuzzing the web application.

@@

The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.

@@

@@

Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

@@

%\begin{table}[tbp]
%	\centering
%	\normalsize
%	\begin{tabular}{|c|c|c|}
%		\hline
%		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
%		\hline
%		1 & PHP, Java, Ruby, etc. & Unix\\
%		\hline
%		2 & PHP, Java, Ruby, etc. & Windows\\
%		\hline
%		3 & Python & Unix\\
%		\hline
%		4 & Python & Windows\\
%		\hline
%	\end{tabular}
%	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
%	\label{tab:payloadcov}
%\end{table}

\begin{table}[tbp]
	\centering
	\normalsize
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
		\hline
		\textbf{PHP, Java, Ruby} & 1 & 3\\
		\hline
		\textbf{Python} & 2 & 4\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular e-mail}
\sloppy
`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.
